---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# timenow

<!-- badges: start -->
<!-- badges: end -->


Quick timezone-aware timestamps for R.

```r
# install.packages("pak")
pak::pak("hypertidy/timenow")  
```

```{r basic}
library(timenow)
# basic usage
timenow()

# fuzzy timezone matching
timenow("Perth")
timenow("new york")
timenow("tokyo")
```

## Why?

When working with vessels or traverses or servers where wall time or
`Sys.timezone()` returns `"UTC"`, it's handy to still see your local time.
`timenow` uses a detection cascade to find your actual timezone.


## Configuration

If your system is UTC, set your timezone with:

```r
timenow_set("Hobart")
# or fuzzy:
timenow_set("Perth Australia")
```

This writes to `~/.Renviron` and takes effect next session (also sets it for the current session).

Or manually add to `~/.Renviron`:

```
R_TIMENOW_TZ=Australia/Hobart
```

Or run `timenow_help()` for more options.

## Timezone detection cascade

1. `getOption("timenow.tz")`
2. `Sys.getenv("R_TIMENOW_TZ")`
3. `/etc/timezone` (Debian/Ubuntu)
4. `timedatectl show --property=Timezone` (systemd)
5. `Sys.timezone()`


## Code of Conduct
  
Please note that the timenow project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

